---
title: "Stock Dynamics"
author: "datadavidz"
date: "February 8, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Analysis of Stocks for Five Major Companies

We'll look at the monthly stock prices of five companies: IBM, General Electric (GE), Procter and Gamble, Coca Cola and Boeing.

* **Date:** the date of the stock price always at the first of the month.
* **StockPrice:** the average stock price of the company in the given month.


```{r cars}
#Read in stock data
IBM <- read.csv("IBMStock.csv")
GE <- read.csv("GEStock.csv")
ProcterGamble <- read.csv("ProcterGambleStock.csv")
CocaCola <- read.csv("CocaColaStock.csv")
Boeing <- read.csv("BoeingStock.csv")
```

### Summary Statistics

First, we need to convert the dates to R format.

```{r dates}
IBM$Date <- as.Date(IBM$Date, "%m/%d/%y")
GE$Date <- as.Date(GE$Date, "%m/%d/%y")
CocaCola$Date <- as.Date(CocaCola$Date, "%m/%d/%y")
ProcterGamble$Date <- as.Date(ProcterGamble$Date, "%m/%d/%y")
Boeing$Date <- as.Date(Boeing$Date, "%m/%d/%y")
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
